### 2015-09-23 Projects/DelCo_2014/Report/Hose_Stream_Report/Report/DelCo_Hose_Tests_2014.tex
DelCo_2014: Generated new figs for report, deleted old figs

\begin{figure}[!ht]
\includegraphics[trim=0cm 0cm 0.25cm 4cm, clip=true, width=6in]{../Drawings/East_Structure_Metric_Simple}
\caption[East Structure Layout]{East Structure floor layout. All dimensions are in meters.}
\label{fig:east_general_plan}
\end{figure}

@@

\begin{figure}[!ht]
\includegraphics[trim=0cm 0cm 0.75cm 4.5cm, clip=true, width=6in]{../Drawings/West_Structure_1st_Floor_Metric_Simple}
\\
\includegraphics[trim=0cm 0cm 0.75cm 5.0cm, clip=true, width=6in]{../Drawings/West_Structure_2nd_Floor_Metric_Simple}
\caption[West Structure First and Second Floor Layout]{West Structure first floor (top) and second floor (bottom) layouts. All dimensions are in meters.}
\label{fig:west_general_plan}
\end{figure}

@@

\subsection{Instrumentation}
\label{subsec:instrumentation}
There is a discussion of uncertainties for each measurement below in Section~\ref{subsec:uncertainty}. Gas velocity was measured at various doorways using differential pressure transducers connected to bi-directional velocity probes (BDPs)~\cite{McCaffrey:Combustion_and_Flame}. Each set of BDPs contained 8 probes located at distances of 0.08 m, 0.34 m, 0.61 m, 0.88 m, 1.15 m, 1.42 m, 1.68 m, and 1.95 m below the soffit of the corresponding doorway. Fig.~\ref{fig:BDPs} shows a picture of two sets of BDPs, A5 and A6, located at each double door on the first floor of the West Structure. To avoid potential measurement errors due to external environmental conditions, only velocity data measured by BDPs located in interior doorways were considered during analyses. Schematic plan overviews of the instrumentation in the East and West Structures are provided in Fig.~\ref{fig:east_devices} and Fig.~\ref{fig:west_devices}. A single thermocouple was attached to each bi-directional probe. The thermocouples that are used with the bi-directional probes are exposed-bead, Chromel-Alumel (type K) with a 1.0 mm (0.04 in) diameter. Starting with the exposed bead, the thermocouple wire was sheathed in a 3.2 mm (0.13 in) diameter Inconel shield, 0.76 m (2.5 ft) in length.

@@

Test 33 involved flowing water from a monitor equipped with a combination nozzle and positioned in Room C through Door BC to Room B of the East Structure (Fig.~\ref{fig:test_33_pic}). A schematic of the structure's layout during the test series is presented in Fig.~\ref{fig:test_33_34_setup}. Test 33 began by flowing water in a straight stream pattern for 30 seconds, then in a narrow fog stream for 30 seconds, and finally in a wide fog stream for 30 seconds. Then, the south side door was opened and each stream was applied for 30 seconds again.

\begin{figure}[!ht]
\begin{overpic}[trim=0cm 0cm 0cm 4.5cm, clip=true, width=6in]{../Drawings/Specific_Tests/East_Structure_Hose_Test_33_34}
	\put(66,36){\includegraphics[width=1in]{../Drawings/monitor_graphic}}
\end{overpic}
\caption[East Structure Layout for Tests 33 and 34]{East Structure layout for Tests 33 and 34}
\label{fig:test_33_34_setup}
\end{figure}
\FloatBarrier

>>>>

\begin{figure}[!ht]
\includegraphics[width=6in]{../Drawings/Specific_Tests/East_Test_Structure_Dimensioned}
\caption[East Structure Layout]{East Structure floor layout.}
\label{fig:east_general_plan}
\end{figure}

@@

\begin{figure}[!ht]
\includegraphics[width=6in]{../Drawings/Specific_Tests/West_Test_Structure_1st_Floor_Dimensioned}
\\
\includegraphics[width=6in]{../Drawings/Specific_Tests/West_Test_Structure_2nd_Floor_Dimensioned}
\caption[West Structure First and Second Floor Layout]{West Structure first floor (top) and second floor (bottom) layouts.}
\label{fig:west_general_plan}
\end{figure}

@@

\subsection{Instrumentation}
\label{subsec:instrumentation}
There is a discussion of uncertainties for each measurement below in Section~\ref{subsec:uncertainty}. Gas velocity was measured at various doorways using differential pressure transducers connected to bi-directional velocity probes (BDPs)~\cite{McCaffrey:Combustion_and_Flame}. The Each set of BDPs contained 8 probes located at distances of 0.08 m, 0.34 m, 0.61 m, 0.88 m, 1.15 m, 1.42 m, 1.68 m, and 1.95 m below the soffit of the corresponding doorway. Fig.~\ref{fig:BDPs} shows a picture of two sets of BDPs, A5 and A6, located at each double door on the first floor of the West Structure. To avoid potential measurement errors due to external environmental conditions, only velocity data measured by BDPs located in interior doorways were considered during analyses. Schematic plan overviews of the instrumentation in the East and West Structures are provided in Fig.~\ref{fig:east_devices} and Fig.~\ref{fig:west_devices}. A single thermocouple was attached to each bi-directional probe. The thermocouples that are used with the bi-directional probes are exposed-bead, Chromel-Alumel (type K) with a 1.0 mm (0.04 in) diameter. Starting with the exposed bead, the thermocouple wire was sheathed in a 3.2 mm (0.13 in) diameter Inconel shield, 0.76 m (2.5 ft) in length.

@@

Test 33 involved flowing water from a monitor equipped with a combination nozzle and positioned in Room C through Door BC to Room B of the East Structure (Fig.~\ref{fig:test_33_pic}). A schematic of the structure's layout during the test series is presented in Fig.~\ref{fig:east_setup}. Test 33 began by flowing water in a straight stream pattern for 30 seconds, then in a narrow fog stream for 30 seconds, and finally in a wide fog stream for 30 seconds. Then, the south side door was opened and each stream was applied for 30 seconds again.

\begin{figure}[!ht]
% \begin{overpic}
\includegraphics[width=6in]{../Drawings/Specific_Tests/East_Hose_Test_Annotated}
% 	\put(66,36){\includegraphics[width=1in]{../Drawings/monitor_graphic}}
% \end{overpic}
\caption[East Structure Layout for Tests 33 and 34]{East Structure layout for Tests 33 and 34}
\label{fig:east_setup}
\end{figure}
\FloatBarrier
